A Double-Sampling Extension of the German National Forest Inventory for Design-Based Small Area Estimation on Forest District Levels

### 2018-08-06 manuscript.v4/remotesensing-311343-proofreading/remotesensing-311343-proofreading.tex
update 06_08_2018
final version of published article

%=================================================================
\documentclass[remotesensing,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi} 
%
%--------------------
% Class Options:
%--------------------
% journal
%----------
% Choose between the following MDPI journals:
% actuators, addictions, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, ceramics, challenges, chemengineering, chemosensors, children, chromatography, climate, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cybersecurity, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electrochemistry, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forests, fractalfract, futureinternet, galaxies, games, gastrointestdisord, gels, genealogy, genes, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, ijtpp, inventions, j, jcdd, jcm, jcs, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmmp, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nitrogen, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, plasma, polymers, preprints, proceedings, processes, proteomes, publications, quaternary, qubs, recycling, religions, remotesensing, resources, risks, robotics, safety, scipharm, sensors, separations, sexes, sinusitis, socsci, societies, soils, sports, standards, surgeries, sustainability, symmetry, systems, technologies, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vetsci, vibration, viruses, vision, water, wem
%---------
% article
%---------
% The default type of manuscript is article, but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferenceproceedings, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, opinion, obituary, projectreport, reply, reprint, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials
% protocol: If you are preparing a "Protocol" paper, please refer to http://www.mdpi.com/journal/mps/instructions for details on its expected structure and content.
%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g. the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother 
\articlenumber{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2017}
\copyrightyear{2017}
\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}

@@

\usepackage[font=footnotesize]{caption}
\usepackage[font=footnotesize]{subcaption}

@@

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{A double-sampling extension of the German National Forest Inventory for design-based small area estimation on forest district levels}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
	$^{1}$ \quad Department of Environmental Systems Science, ETH Zurich, 8092 Zurich, Switzerland; mdaniel@retired.ethz.ch (D.M.)\\
	$^{2}$ \quad State Forest Service Rhineland-Palatinate, 56281 Emmelshausen, Germany; Joachim.Langshausen@wald-rlp.de}

% Contact information of the corresponding author
\corres{Correspondence: andreas.hill@usys.ethz.ch; Tel.: +x-xxx-xxx-xxxx}

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval. However, the data have yet been scarcely used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors. In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area regression estimators. We illustrate the implementation of the estimation procedure and evaluate its potential for future large-scale operational application by the example of timber volume estimation on two small-scale management levels (45 and 405 forest district units respectively) over the entire area of the federal German state of Rhineland-Palatinate. An airborne laserscanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least square regression model to produce the timber volume predictions. The results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels: the two-phase estimators were able to reduce the variance of the one-phase simple random sampling estimator by 43\% and 25\% on average for the two management levels respectively.}

% Keywords
\keyword{National forest inventory, small area estimation, forest districts, double sampling for regression within strata, cluster sampling, canopy height model, tree species classification}

@@

The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germany's forest over time. The NFI thereby has the responsibility to satisfy various information needs including reporting to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and to the United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}. The current design of the German NFI rests solely upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forested area of Germany. In order to cover a large area of 114'191 km$^2$ \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels. However, sample sizes often drop dramatically when entering spatial units below the federal state level. This is particularly true for forest management levels such as forest districts for which the estimation uncertainties turn out to be unacceptably large due to the very limited number of sample plots within these units. For this reason, the German NFI data have not yet been extensively incorporated into operational planning on forest district management levels. In most German federal states, management strategies are thus still based on expert judgements from time-consuming standwise forest inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par

@@

Double-sampling procedures have already been used in various countries such as Canada \citep{gillis2010intomppo}, the USA \citep{chojnacky1998}, Switzerland \citep{lanz2010intomppo}, Italy \citep{gasparini2010intomppo} and Germany \citep{saborowski2010}. Recent studies from \citet{grafstrom2017a} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs. Double-sampling has also been extended to triple-sampling estimation methods using auxiliary information derived at two different sampling intensities. An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI of Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories. Another example is \citet{massey2014a} who developed a triple-sampling extension based on the ideas of \citet{mandallaz2013c} for the Swiss NFI that can significantly reduce the increase in estimation uncertainty caused by the new annual inventory design.\par

Two-phase and three-phase samplings techniques have also been applied to small area estimation (SAE). SAE techniques address the situation where the number of samples within a subunit, or small area (SA), of the entire sampling frame is too small to provide reliable estimates for that unit. A broad range of SA estimators used in forest inventories \citep{kohl2006} originally comes from official statistics. One such method that is commonly applied is known as indirect estimation \citep{rao2015}, where statistical models are used to convert auxiliary information into predictions of the target variable that is rarely or not observed in the small area. These models are trained using data from outside the small area in order to "borrow strength" from areas where information is available. Of numerous applications of SAE in forestry \citep{breidenbach2012, goerndt2011, steinmann2013, mandallaz2013b}, most use unit-level models, i.e. the inventory plot is the unit of the response variable in the training data used for the model fit. Such unit-level models have been intensively investigated for timber volume estimation using various remote sensing auxiliary data \citep{koch2010, naesset2014inmaltamo}. Other studies have investigated area-level models, where the auxiliary information is only provided on the SA level \citep{magnussen2017}. Some studies have illustrated that even NFI data derived under low sampling densities can still be used to provide acceptable precision of small area estimates on much smaller management levels. One example is \citet{breidenbach2012} who used data from the Norwegian NFI to make small area estimation for standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35. The estimation errors under the applied model-dependent and design-based small area estimators turned to be markedly smaller than under the standard one-phase estimator. Another example is \citet{magnussen2014} who recently used the Swiss NFI data to estimate timber volume within 108 Swiss forest districts with sample sizes between 9 and 206. Similar studies using German NFI data for small area estimation have been lacking.\par

The objective of this study was to investigate whether the application of latest design-based small area estimation methods allow to use the German NFI data to produce estimates of acceptable precision on two forest district levels. The methods were tested in the German federal state Rhineland-Palatinate. Three types of model-assisted design-based small area regression estimators were used to derive point and variance estimates of mean standing timber volume for 45 and 405 forest management units on the two respective district levels. The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested by \citet{mandallaz2013a} and \citet{ mandallaz2013b}. Auxiliary data consisted of a canopy height model (CHM) obtained from a countrywide airborne laser scanning (ALS) and a tree species classification map to be used for regression within tree species strata. The estimation precisions were compared to those obtained by the standard one-phase estimator for cluster sampling under simple random sampling. The chosen double-sampling estimators were selected for several reasons: \textbf{(i)} the design-based framework relaxes dependencies on the regression model assumptions which seemed appropriate facing severe quality restrictions in the ALS data; \textbf{(ii)} the estimators can be used with \textit{non-exhaustive}, i.e. non wall-to-wall, auxiliary information; \textbf{(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators; and \textbf{(iv)} the asymptotically unbiased g-weight variance partially accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust under heteroscedasticity of the model residuals. The results from this study were considered to provide valuable information about the potential of the suggested small area estimation procedure and the incorporated auxiliary information for future operational large scale application.\par

@@

\section{Terrestrial sampling design of the German NFI}
\label{sec:germanNFI}

The German NFI (Bundeswaldinventur, BWI )is a periodic inventory that is carried out every 10 years over the entire forest area of Germany. The third and most recent inventory (BWI3) was conducted in 2011 and 2012. While information was originally gathered on a systematic 4x4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2x2 km grid. The German NFI uses a cluster sampling design, which means that a sample unit consists of at most four sample locations (also referred to as \textit{sample plots}) that are arranged in a square, called \textit{cluster}, with a side length of 150 metres. The number of plots per cluster can vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}. In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}. Angle count sampling is a visual selection procedure conducted via an optical instrument (\textit{Relascope}). At a sample point $x$, a tree is selected as a sample tree if its apparent diameter at the height of 1.3 m ($DBH$) and the associated angle $\alpha_i$ (in radiant) appears larger than a limit angle $\alpha$ when viewed through the Relascope \citep{mandallaz2008}. The limit angle $\alpha{}$ can be expressed by the so-called basal area factor ($BAF$), i.e. $BAF = 10^{2}sin^{2}(\frac{\alpha}{2})$. Consequently, each tree $i$ is assigned with an individual radius $R_{i}=\frac{DBH_{i}}{2\sqrt{BAF}}$ which is the distance between the tree location and the sample plot center. A tree is selected if $R_{i}$ is equal to or smaller than the so-called limiting distance $R$ that results from chosen BAF (i.e., $\alpha$). One characteristic of angle count sampling is that a sample plot does no longer has a fixed radius in which sample trees are selected, but each tree creates its individual radius $R_i$ that is - likewise the associated inclusion probability - proportional to its basal area. For this reason, the angle count method is also referred to as \textit{variable radius plot sampling} and implements the \textit{probability proportional to size (PPS)} concept. The BWI3 uses a basal area factor of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the individual tree's inclusion circle \citep{bwi3_aufn}. A further inventory threshold for a tree to be recorded is a DBH of at least 7 cm. For each sample tree that is selected by this procedure, the DBH, the absolute tree height, the tree diameter at 7 m ($D7$) and the tree species is measured and used to estimate the volume at the tree level. These volume estimates are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.

% ++++++++++++ %
\section{Double sampling in the infinite population approach}
\label{sec:inf_pop}

 \subsubsection{One- and Two-Phase Sampling in the Infinite Population Approach}

>>>>

% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
\documentclass[remotesensing,article,accept,moreauthors,pdftex,10pt,a4paper]{Definitions/mdpi} 
%
%--------------------
% Class Options:
%--------------------
% journal
%----------
% Choose between the following MDPI journals:
% actuators, addictions, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, ceramics, challenges, chemengineering, chemosensors, children, chromatography, climate, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cybersecurity, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electrochemistry, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forests, fractalfract, futureinternet, galaxies, games, gastrointestdisord, gels, genealogy, genes, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, ijtpp, inventions, j, jcdd, jcm, jcs, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmmp, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nitrogen, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, plasma, polymers, preprints, proceedings, processes, proteomes, publications, quaternary, qubs, recycling, religions, remotesensing, resources, risks, robotics, safety, scipharm, sensors, separations, sexes, sinusitis, socsci, societies, soils, sports, standards, surgeries, sustainability, symmetry, systems, technologies, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vetsci, vibration, viruses, vision, water, wem
%---------
% article
%---------
% The default type of manuscript is article, but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferenceproceedings, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, opinion, obituary, projectreport, reply, reprint, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile  =  supplementary materials
% protocol: If you are preparing a "Protocol" paper, please refer to http://www.mdpi.com/journal/mps/instructions for details on its expected structure and content.
%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g. the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{1}
\pubyear{2018}
\copyrightyear{2018}
%\externaleditor{Academic Editor: name}
\history{Received: 17 May 2018; Accepted: 26 June 2018; Published: date}

@@

\usepackage[font = footnotesize]{caption}
\usepackage[font = footnotesize]{subcaption}

@@

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput = 1

% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

% =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  =  = 
% Full title of the paper (Capitalized)
\Title{A Double-Sampling Extension of the German National Forest Inventory for Design-Based Small Area Estimation on Forest District Levels}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
	$^{1}$ \quad Department of Environmental Systems Science, ETH Zurich, 8092 Zurich, Switzerland; mdaniel@retired.ethz.ch\\
	$^{2}$ \quad State Forest Service Rhineland-Palatinate, 56281 Emmelshausen, Germany; Joachim.Langshausen@wald-rlp.de}

% Contact information of the corresponding author
\corres{Correspondence: andreas.hill@usys.ethz.ch}

% Abstract (Do not insert blank lines, i.e.,~\\) 
\abstract{The German National Forest Inventory consists of a systematic grid of permanent sample plots and provides a reliable evidence-based assessment of the state and the development of Germany's forests on national and federal state level in a 10 year interval. However, the data have yet been scarcely used for estimation on smaller management levels such as forest districts due to insufficient sample sizes within the area of interests and the implied large estimation errors. In this study, we present a double-sampling extension to the existing German National Forest Inventory (NFI) that allows for the application of recently developed design-based small area regression estimators. We illustrate the implementation of the estimation procedure and evaluate its potential for future large-scale operational application by the example of timber volume estimation on two small-scale management levels (45 and 405 forest district units respectively) over the entire area of the federal German state of Rhineland-Palatinate. An airborne laserscanning (ALS) derived canopy height model and a tree species classification map based on satellite data were used as auxiliary data in an ordinary least square regression model to produce the timber volume predictions. The~results support that the suggested double-sampling procedure can substantially increase estimation precision on both management levels: the two-phase estimators were able to reduce the variance of the one-phase simple random sampling estimator by 43\% and 25\% on average for the two management levels~respectively.}

% Keywords
\keyword{National Forest Inventory; small area estimation; forest districts; double sampling for regression within strata; cluster sampling; canopy height model; tree species classification}

@@

The German National Forest Inventory (NFI) provides reliable evidence-based and accurate information of the current state and the development of Germany's forest over time. The NFI thereby has the responsibility to satisfy various information needs including reporting to public and state forestry administrations, wood-based industries and the public on the national level, as well as to the Food and Agriculture Organization of the United Nations (FAO) and to the United Nations Framework Convention on Climate Change (UNFCC) on the international level \citep{polley2010intomppo}. The current design of the German NFI rests solely upon a terrestrial cluster inventory that is carried out at sample locations systematically distributed over the entire forested area of Germany. In order to cover a large area of 114,191 km$^2$ \citep{bwi3}, the sample size has been specifically chosen to satisfy high estimation accuracies for forest attributes on the national and federal state levels. However, sample sizes often drop dramatically when entering spatial units below the federal state level. This is particularly true for forest management levels such as forest districts for which the estimation uncertainties turn out to be unacceptably large due to the very limited number of sample plots within these units. For this reason, the German NFI data have not yet been extensively incorporated into operational planning on forest district management levels. In most German federal states, management strategies are thus still based on expert judgements from time-consuming standwise forest inventories (SFI), which are prone to systematic deviations \cite{kulievsis2016} and do not provide any measure of uncertainty.\par

@@

Double-sampling procedures have already been used in various countries such as Canada \citep{gillis2010intomppo}, the USA \citep{chojnacky1998}, Switzerland \citep{lanz2010intomppo}, Italy \citep{gasparini2010intomppo} and Germany \citep{saborowski2010}. Recent studies \mbox{from \citet{grafstrom2017a}} illustrated how to use the auxiliary information to determine optimised balanced terrestrial sample designs. Double-sampling has also been extended to triple-sampling estimation methods using auxiliary information derived at two different sampling intensities. An example can be found in \citet{vonLuepke2012} who illustrated an extension of the existing two-phase FDI of Lower Saxony to a three-phase design that uses updates of past inventory data as additional auxiliary information and allows for a significant reduction of the terrestrial sample size in intermediate inventories. Another example is \citet{massey2014a} who developed a triple-sampling extension based on the ideas of \citet{mandallaz2013c} for the Swiss NFI that can significantly reduce the increase in estimation uncertainty caused by the new annual inventory design.\par

Two-phase and three-phase samplings techniques have also been applied to small area estimation (SAE). SAE techniques address the situation where the number of samples within a subunit, or small area (SA), of the entire sampling frame is too small to provide reliable estimates for that unit. A~broad range of SA estimators used in forest inventories \citep{kohl2006} originally comes from official statistics. One~such method that is commonly applied is known as indirect estimation \citep{rao2015}, where statistical models are used to convert auxiliary information into predictions of the target variable that is rarely or not observed in the small area. These models are trained using data from outside the small area in order to ``borrow strength'' from areas where information is available. Of numerous applications of SAE in forestry \citep{breidenbach2012, goerndt2011, steinmann2013, mandallaz2013b}, most use unit-level models, i.e.,~the inventory plot is the unit of the response variable in the training data used for the model fit. Such unit-level models have been intensively investigated for timber volume estimation using various remote sensing auxiliary data \citep{koch2010, naesset2014inmaltamo}. Other studies have investigated area-level models, where the auxiliary information is only provided on the SA level \citep{magnussen2017}. Some studies have illustrated that even NFI data derived under low sampling densities can still be used to provide acceptable precision of small area estimates on much smaller management levels. One~example is \citet{breidenbach2012} who used data from the Norwegian NFI to make small area estimation for standing timber volume for 14 municipalities where the number of NFI samples within these areas were between 1 and 35. The estimation errors under the applied model-dependent and design-based small area estimators turned to be markedly smaller than under the standard one-phase estimator. Another example is \citet{magnussen2014} who recently used the Swiss NFI data to estimate timber volume within 108 Swiss forest districts with sample sizes between 9 and 206. Similar studies using German NFI data for small area estimation have been lacking.\par

The objective of this study was to investigate whether the application of latest design-based small area estimation methods allow to use the German NFI data to produce estimates of acceptable precision on two forest district levels. The methods were tested in the German federal state Rhineland-Palatinate. Three types of model-assisted design-based small area regression estimators were used to derive point and variance estimates of mean standing timber volume for 45 and 405 forest management units on the two respective district levels. The SA-estimators we considered were the \textit{pseudo-small}, \textit{extended pseudo-synthetic} and the \textit{pseudo-synthetic} design-based small area estimator suggested \mbox{by \citet{mandallaz2013a}} and \citet{ mandallaz2013b}. Auxiliary data consisted of a canopy height model (CHM) obtained from a countrywide airborne laser scanning (ALS) and a tree species classification map to be used for regression within tree species strata. The estimation precisions were compared to those obtained by the standard one-phase estimator for cluster sampling under simple random sampling. The chosen double-sampling estimators were selected for several reasons: {(i)} the design-based framework relaxes dependencies on the regression model assumptions which seemed appropriate facing severe quality restrictions in the ALS data; {(ii)} the estimators can be used with \textit{non-exhaustive}, i.e.,~non wall-to-wall, auxiliary information; {(iii)} all estimators are explicitly formulated for cluster sampling which has not yet been the case for frequently used model-dependent estimators and {(iv)} the asymptotically unbiased g-weight variance partially accounts for estimating the regression coefficients on the same sample used for estimation (\textit{internal model approach}) and is also robust under heteroscedasticity of the model residuals. The results from this study were considered to provide valuable information about the potential of the suggested small area estimation procedure and the incorporated auxiliary information for future operational large scale application.\par

@@

\section{Terrestrial Sampling Design of the German NFI}
\label{sec:germanNFI}

The German NFI (Bundeswaldinventur, BWI) is a periodic inventory that is carried out every 10 years over the entire forest area of Germany. The third and most recent inventory (BWI3) was conducted in 2011 and 2012. While information was originally gathered on a systematic 4 $\times$ 4 km grid, some federal states such as Rhineland-Palatinate have switched to a densified 2 $\times$ 2 km grid. The German NFI uses a cluster sampling design, which means that a sample unit consists of at most four sample locations (also referred to as \textit{sample plots}) that are arranged in a square, called \textit{cluster}, with a side length of 150 metres. The number of plots per cluster can vary between 1 and 4 depending on forest/non-forest decisions by the field crews on the individual plot level \citep{bwi3_aufn}. In the field survey of the BWI3, sample trees for timber volume estimation are selected according to the angle count sampling technique \citep{bitterlich1984}. Angle count sampling is a visual selection procedure conducted via an optical instrument (\textit{Relascope}). At a sample point $x$, a tree is selected as a sample tree if its apparent diameter at the height of 1.3 m ($DBH$) and the associated angle $\alpha_i$ (in radiant) appears larger than a limit angle $\alpha$ when viewed through the Relascope \citep{mandallaz2008}. The limit angle $\alpha{}$ can be expressed by the so-called basal area factor ($BAF$), i.e.,~$BAF  =  10^{2}sin^{2}(\frac{\alpha}{2})$. Consequently, each tree $i$ is assigned with an individual radius $R_{i} = \frac{DBH_{i}}{2\sqrt{BAF}}$ which is the distance between the tree location and the sample plot center. A tree is selected if $R_{i}$ is equal to or smaller than the so-called limiting distance $R$ that results from chosen BAF (i.e., $\alpha$). One characteristic of angle count sampling is that a sample plot does no longer has a fixed radius in which sample trees are selected, but each tree creates its individual radius $R_i$ that is - likewise the associated inclusion probability - proportional to its basal area. For this reason, the angle count method is also referred to as \textit{variable radius plot sampling} and implements the \textit{probability proportional to size (PPS)} concept. The BWI3 uses a basal area factor of 4 that is respectively adjusted for sample trees at the forest boundary by a geometric intersection of the boundary transect with the individual tree's inclusion circle \citep{bwi3_aufn}. A further inventory threshold for a tree to be recorded is a DBH of at least 7 cm. For each sample tree that is selected by this procedure, the DBH, the absolute tree height, the~tree diameter at 7 m ($D7$) and the tree species is measured and used to estimate the volume at the tree level. These volume estimates are based on the application of tree species specific taper curves that are adjusted to the set of diameters and corresponding height measurements taken from the respective sample tree \citep{kublin2013}.

% ++++++++++++ %
\section{Double Sampling in the Infinite Population Approach}
\label{sec:inf_pop}
\vspace{-6pt}

% \subsection*{One- and Two-Phase Sampling in the Infinite Population Approach} [Please remove this header if possible (redundant with main section title)]

The estimators used in this study have been proposed by \citep{mandallaz2013a,mandallaz2013b} and derive their mathematical properties under the so-called infinite population approach. Therefore, we shall first provide a short introduction into this general estimation framework. We start by assuming that the population $P$ of trees $i \in 1,2, ..., N$ within a forest of interest $F$ is exactly defined, and each tree $i$ has a response variable $Y_i$ (e.g., its timber volume) that can be used to define the population mean $Y$ (e.g., the average timber volume per unit area) over $F$. Since a full census of all tree population individuals is almost never feasible, $Y$ has to be estimated based on a sample. In the infinite population approach this sample is a set of points or locations $x$ distributed independently and uniformly over the set of all possible points in $F$. Each point $x$ has an associated local density $Y(x)$ (e.g., the timber volume per unit area) whose spatial distribution is given by a fixed (i.e.,~non stochastic) piecewise constant function. The population mean $Y$ is mathematically equivalent to the integral of the local density function surface divided by the surface area of $F$, $\lambda(F)$, i.e.,~$Y = \frac{1}{N} \sum_{i = 1}^{N}Y_i = \frac{1}{\lambda(F)}\int_{F}Y(x)dx$, and thus the population mean $Y$ corresponds to a spatial mean. Since the actual local density function is unobserved in its entirety, one estimates $Y$ by taking a sample $s_2$ consisting of $n_2$ points and measuring each of their respective local densities. This sampling procedure is often referred to as \textit{one-phase sampling} (OPS) and $s_2$ is referred to as the terrestrial inventory. In contrast to the one-phase approach, \textit{two-phase} or \textit{double-sampling} procedures use information from two nested samples (phases). Practically speaking, the terrestrial inventory $s_2$ is embedded in a large phase $s_1$ comprising $n_1$ sample locations that each provide a set of explanatory variables described by the column vector $\pmb{Z}(x) = (z(x)_1, z(x)_2,...,z(x)_p)^{\top}$ at each point $x \in s_1$. These explanatory variables are derived from auxiliary information that is available in high quantity within the forest $F$. For every $x \in s_1$, $\pmb{Z}(x)$ is transformed into a prediction $\hat{Y}(x)$ of $Y(x)$ using the choice of some prediction model. The basic idea of this method is to boost the sample size by providing a large sample of less precise but cheaper predictions of $Y(x)$ in $s_1$ and to correct any possible model bias, i.e.,~$\EX{(Y(x)-\hat{Y}(x))}$, using the subsample of terrestrial inventory units where the value of $Y(x)$ is observed. In this context, it is also important to note that the response and auxiliary variables are assumed to be error-free and the resulting errors for the point estimates reflect only the uncertainty due to sampling.
